---
title: "OT minus P rewrite"
output: html_notebook
---
---
title: "O_T_minus_P_I_take2"
output: html_notebook
---

*Kate Dixon, 2019*

Script to subtract parental interaction/interference bouts (P) from infant on-task bouts (O_T) if they occur at the same time or overlap. Writes new duration times per O_T bout (minus P or part of P bout if appropriate) to new csv file. 

*CHANGE FILE NUMBER IN TWO CHUNKS*

## Clear environment
```{r}
remove(list = ls())
```

## Set working directory
```{r}
setwd("C:/Users/Kate/Desktop")
```

## Load packages
```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(plyr)
library(readxl)
```

## Load data- *CHANGE NAME OF FILE HERE*
```{r load-data}
df <- read.csv("228903.csv", header=TRUE)
df <- as.data.frame(df)
```

## Creating separate dataframes for on task times (allO_T) and for parent interaction times (all_P). Also initializing empty df for output of loop in next chunk.
```{r}
new_O_T_durations <- data.frame(matrix(vector(), (dim(df)[1]), 1))

O_Ton <- select(df,O_T.onset)
O_Toff <- select(df, O_T.offset)
allO_T <- cbind(O_Toff, O_Ton)
allO_T[is.na(allO_T)] <- 0

P_on <- select(df, P.onset)
P_off <- select(df, P.offset)
all_P <- cbind(P_off, P_on)
all_P <- all_P[complete.cases(all_P), ]
```

## Loop to determine if PI bouts (or part of the bouts) need to be subtracted from the on-task bouts. Puts new on-task durations in new df (new_O_T_durations).
*vectorize later*
```{r}
for (i in 1:dim(allO_T)[1]){
      for(j in 1:dim(all_P)[1]){
            if ((all_P$P.onset[j] > allO_T$O_T.onset[i]) & (all_P$P.offset[j] < allO_T$O_T.offset[i]) & (all_P$P.offset[j] > allO_T$O_T.onset[i]) & (all_P$P.onset[j] < allO_T$O_T.offset[i]) & (all_P$P.onset[j+1] > allO_T$O_T.offset[i]) & (all_P$P.offset[j+1] > allO_T$O_T.offset[i])){ #1
                new_O_T_durations[i,j] = ((allO_T$O_T.offset[i] - allO_T$O_T.onset[i]) - (all_P$P.offset[j] - all_P$P.onset[j]))
            }
            else if ((all_P$P.onset[j] < allO_T$O_T.onset[i]) & (all_P$P.offset[j] < allO_T$O_T.offset[i]) & (all_P$P.offset[j] > allO_T$O_T.onset[i]) & (all_P$P.onset[j] < allO_T$O_T.offset[i]) & (all_P$P.onset[j+1] > allO_T$O_T.offset[i]) & (all_P$P.offset[j+1] > allO_T$O_T.offset[i])){ #2
                  new_O_T_durations[i,j] = allO_T$O_T.offset[i] - all_P$P.offset[j]
            }
            else if ((all_P$P.onset[j] < allO_T$O_T.onset[i]) & (all_P$P.offset[j] > allO_T$O_T.offset[i]) & (all_P$P.offset[j] > allO_T$O_T.onset[i]) & (all_P$P.onset[j] < allO_T$O_T.offset[i]) & (all_P$P.onset[j+1] > allO_T$O_T.offset[i]) & (all_P$P.offset[j+1] > allO_T$O_T.offset[i])){ #4
                  new_O_T_durations[i,j] = 0
            }
            else if ((all_P$P.onset[j] > allO_T$O_T.onset[i]) & (all_P$P.offset[j] < allO_T$O_T.offset[i]) & (all_P$P.offset[j] > allO_T$O_T.onset[i]) & (all_P$P.onset[j] < allO_T$O_T.offset[i]) & (all_P$P.onset[j+1] < allO_T$O_T.offset[i]) & (all_P$P.offset[j+1] < allO_T$O_T.offset[i])){ #5
                  new_O_T_durations[i,j] = (allO_T$O_T.offset[i] - allO_T$O_T.onset[i]) - (all_P$P.offset[j] - all_P$P.onset[j]) - (all_P$P.offset[j+1] - all_P$P.onset[j+1])
            }
            else if ((all_P$P.onset[j] > allO_T$O_T.onset[i]) & (all_P$P.offset[j] < allO_T$O_T.offset[i]) & (all_P$P.offset[j] > allO_T$O_T.onset[i]) & (all_P$P.onset[j] < allO_T$O_T.offset[i]) & (all_P$P.onset[j+1] < allO_T$O_T.offset[i]) & (all_P$P.offset[j+1] > allO_T$O_T.offset[i])){ #6
                  new_O_T_durations[i,j] = (allO_T$O_T.offset[i] - allO_T$O_T.onset[i]) - (all_P$P.offset[j] - all_P$P.onset[j]) - (allO_T$O_T.offset[i] - all_P$P.onset[j+1])
            }
            else if ((all_P$P.onset[j] < allO_T$O_T.onset[i]) & (all_P$P.offset[j] < allO_T$O_T.offset[i]) & (all_P$P.offset[j] > allO_T$O_T.onset[i]) & (all_P$P.onset[j] < allO_T$O_T.offset[i]) & (all_P$P.onset[j+1] < allO_T$O_T.offset[i]) & (all_P$P.offset[j+1] < allO_T$O_T.offset[i])){ #7
                  new_O_T_durations[i,j] = (all_P$P.onset[j+1] - all_P$P.offset[j]) + (allO_T$O_T.offset[i] - all_P$P.offset[j+1])
            }
            else if ((all_P$P.onset[j] < allO_T$O_T.onset[i]) & (all_P$P.offset[j] < allO_T$O_T.offset[i]) & (all_P$P.offset[j] > allO_T$O_T.onset[i]) & (all_P$P.onset[j] < allO_T$O_T.offset[i]) & (all_P$P.onset[j+1] < allO_T$O_T.offset[i]) & (all_P$P.offset[j+1] > allO_T$O_T.offset[i])){ #8
                  new_O_T_durations[i,j] = all_P$P.onset[j+1] - all_P$P.offset[j]
            }
            else if ((all_P$P.onset[j] >= allO_T$O_T.onset[i]) & (all_P$P.offset[j] > allO_T$O_T.offset[i]) & (all_P$P.offset[j] > allO_T$O_T.onset[i]) & (all_P$P.onset[j] < allO_T$O_T.offset[i]) & (all_P$P.onset[j+1] > allO_T$O_T.offset[i]) & (all_P$P.offset[j+1] > allO_T$O_T.offset[i])){ #9
                  new_O_T_durations[i,j] = all_P$P.onset[j] - allO_T$O_T.onset[i]
            }
            else new_O_T_durations[i,j] = allO_T$O_T.offset[i] - allO_T$O_T.onset[i] #11
      }
}

```

## Getting one value for each O_T bout duration
```{r}
new_O_T_durations2 <- apply(new_O_T_durations, 1, FUN=min)
```

## Adding on task bout number to new duration df
```{r}
O_Tnum <- select(df, O_T.code01)
new_O_T_durations2 <- cbind(new_O_T_durations2, O_Tnum)
```

## Write new_O_T_durations to CSV file *CHANGE NAME OF FILE HERE*
```{r}
write.csv(new_O_T_durations2, file = "228903 newOTdurations.csv",row.names=FALSE)
```

