---
title: "(O_T)-(P_I), O_T_revamp"
output: html_notebook
---

## Clear environment
```{r}
remove(list = ls())
```

## Set working directory
```{r}
setwd("C:/Users/Kate/Desktop/OT minus P script")
```

## Load packages
```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(plyr)
library(readxl)
```

## Load data- *CHANGE NAME OF FILE HERE*
```{r load-data}
df <- read.csv("230433 PROBLEM copy.csv", header=TRUE)
df <- as.data.frame(df)
df[is.na(df)] <- 0
```

## Data reduction - Getting on task/parent interaction times and changing them into seconds and rounding to 2 decimal places.
```{r}
O_Ton <- select(df,O_T.onset)
O_Ton <- O_Ton[as.logical(rowSums(O_Ton != 0)), ]

O_Toff <- select(df, O_T.offset)
O_Toff <- O_Toff[as.logical(rowSums(O_Toff != 0)), ]


O_Ton <- (O_Ton/1000)
O_Ton <- format(round(O_Ton, 2), nsmall = 2)
O_Ton <- as.numeric(O_Ton)

O_Toff <- (O_Toff/1000)
O_Toff <- format(round(O_Toff, 2), nsmall = 2)
O_Toff <- as.numeric(O_Toff)

allO_T <- cbind(O_Toff, O_Ton)
allO_T[is.na(allO_T)] <- 0
allO_T <- allO_T[as.logical(rowSums(allO_T != 0)), ]

P_on <- select(df, P.onset)
P_on <- P_on[as.logical(rowSums(P_on != 0)), ]
P_off <- select(df, P.offset)
P_off <- P_off[as.logical(rowSums(P_off != 0)), ]


P_on <- (P_on/1000)
P_on <- format(round(P_on, 2), nsmall = 2)
P_on <- as.numeric(P_on)

P_off <- (P_off/1000)
P_off <- format(round(P_off,2), nsmall = 2)
P_off <- as.numeric(P_off)

all_P <- cbind(P_off, P_on)
all_P[is.na(all_P)] <- 0
all_P <- all_P[as.logical(rowSums(all_P != 0)), ]
all_P <- all_P[complete.cases(all_P), ]

all_P <- as.data.frame(all_P)
allO_T <- as.data.frame(allO_T)

```

## Creating list of times for "marked_time" dataframe. 
```{r}

a <- allO_T[1,2]
z <- allO_T[(dim(allO_T)[1]),1]

a <- as.numeric(a)
a <- floor(a)

z <- as.numeric(z)
z <- ceiling(z)

x <- a:z

marked_time <- data.frame(matrix(0, nrow = length(x), ncol = 3))
O_Tfinal <- data.frame(matrix(0, nrow = length(x), ncol = 1))
Pfinal <- data.frame(matrix(0, nrow = length(x), ncol = 1))

names(marked_time) <- c("Time_sec", "O_T", "P_I")

marked_time$Time_sec <- x

```

## Marking O_T column in marked_time dataframe with a 1 if an O_T bout is occuring during that time
```{r}
for (i in 1:dim(marked_time)[1]){
      for (j in 1:dim(allO_T)[1]){
            if ((marked_time$Time_sec[i] <= allO_T$O_Toff[j]) & (marked_time$Time_sec[i] >= allO_T$O_Ton[j])){
            O_Tfinal[i,j] = 1
            }
            else O_Tfinal[i,j] = 0
      }
}

O_Tsum <-apply(O_Tfinal,1,sum)
marked_time$O_T <- O_Tsum
total_duration_O_Tsecs <- sum(marked_time$O_T)

```

## Marking P_I column in marked_time dataframe with a 2 if a P_I bout is occuring during that time
```{r}
for (i in 1:dim(marked_time)[1]){
      for (j in 1:dim(all_P)[1]){
            if ((marked_time$Time_sec[i] <= all_P$P_off [j]) & (marked_time$Time_sec[i] >= all_P$P_on [j])){
            Pfinal[i,j] = 2
            }
            else Pfinal[i,j] = 0
      }
}

Pfinalsum <-apply(Pfinal,1,sum)
marked_time$P_I <- Pfinalsum
```

## Getting duration for O_T minus P_I
```{r}
marked_time <- marked_time[marked_time[,3] < 2,]
duration_O_TminusPsecs <- sum(marked_time$O_T)
```

## Combining both durations into one matrix
```{r}
both_durations <- cbind(total_duration_O_Tsecs, duration_O_TminusPsecs)
```

## Write new_O_T_durations to CSV file *CHANGE NAME OF FILE HERE*
```{r}
write.csv(both_durations, file = "230433 PROBLEM copy both_durations.csv",row.names=FALSE)
```