---
title: "OT_P_together"
output: html_notebook
---

*Kate Dixon - 2019*


## Set working directory
```{r}
setwd("C:/Users/Kate/Desktop")
```

## Load packages
```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(plyr)
library(readxl)
library(tidyr)

```

## Load data- *CHANGE NAME OF FILE HERE*
```{r load-data}
df <- read.csv("234580.csv", header=TRUE)
df <- as.data.frame(df)
```

## All O_T onset and offset times in one column ("Time") and trial number and type in 2nd column ("Trialnum") in order by column #1 (final is df allO_T2)
```{r}
O_Ton <- select(df,O_T.onset,O_T.code01)
O_Toff <- select(df, O_T.offset,O_T.code01)
names(O_Ton) <- c("Time","Trialnum")
names(O_Toff) <- c("Time","Trialnum")

allO_T <- rbind(O_Ton, O_Toff)

allO_T2 <- allO_T[order(allO_T$Time),]
```

## All P onset and offset times in one column ("Time") and trial number and type in 2nd column ("Trialnum") in order by column #1 (final is df allP2)
```{r}
Pon <- select(df,P.onset,P.code01)
Poff <- select(df, P.offset,P.code01)

Pon <- Pon[complete.cases(Pon), ]
Poff <- Poff[complete.cases(Poff), ]

names(Pon) <- c("Time","Trialnum")
names(Poff) <- c("Time","Trialnum")

allP <- rbind(Pon, Poff)

allP2 <- allP[order(allP$Time),]
```

## All OT and P onset/offset times in one column (Time) and all trial numbers and types in 2nd column ("Trialnum") in order by column #1 (final is OTandP)
```{r}
OTandP <- rbind(allO_T2, allP2)
OTandP <- OTandP[order(OTandP$Time),]
```

```{r}
write.csv(OTandP, file = "234580 OTandP.csv",row.names=FALSE)
```


